Compositional equivalences based on Open pNets

### 2020-02-18 2016-Weak-FH-Bisim/WeakBisim.tex
corrections de jeudi dernier...

Fig. \ref{SimpleProt:Spec} (left) shows the example principle: two unspecified
processes $P$ and $Q$ (holes) communicate messages, with a data value
argument, through the two protocol entities. Process $P$ send an $\texttt{p\_send(m)}$ message to the $Sender$; this communication is denoted as $\texttt{\underline{in(m)}}$, where underline actions represent internal actions (similar to the $\tau$ of CCS), that cannot be further synchronised with the environment. At the other end process $Q$ receives the message from the $Receiver$. The holes $P$ and $Q$ can also have other interactions with their environment, represented here by actions $\texttt{p\_a}$ and $\texttt{q\_b}$. The underlying network is modelled by a medium entity transporting messages from the sender to the receiver, and that is able to detect transport errors, and signal them to the sender. The return $ack$ message from $receiver$ to $sender$ is supposed to be safe. The final transmission of the message to the recipient (the hole Q) includes the value of the ``error counter'' $ec$.

Fig. \ref{SimpleProt:Spec} (right) shows a graphical view of the pNet of the system \emph{specification}:
the full system should be equivalent (e.g. through weak bisimulation)
to the two processes connected simply through a perfect medium.  
The pNet has a tree-like structure.  The root node of the tree {\it SimpleSystemSpec} is the top level of the pNet structure. It acts as the parallel operator. It consists of tree nodes: two Holes $P$ and $Q$ and one subnet, noted {\it PrefectBuffer}. Nodes of the tree are synchronized using four synchronization vectors, that  express the possible synchronization between the parameterized actions of a subset of the nodes. For instance, in the vector "$< \texttt{p\_send(m)},\texttt{in(m)},\_> \rightarrow \texttt{\underline{in(m)}}$ only $P$ and {\it PrefectBuffer} nodes are involved in the synchronization. More precisely, the synchronization between these processes occurs when  process $P$  performs $\texttt{p\_send(m)}$  action sending a message, and  the medium accepts the message through $\texttt{in(m)}$ action  at the same time. And the result that will be returned at upper level is the internal action  $\texttt{\underline{in(m)}}$.

@@

\begin{example}
  Figure \ref{WOT2} shows the construction of one of the weak transitions of the Specification OA. On the top we show the subset of the original open automaton (from Figure \ref{SimpleProtCounter:SpecOA}) considered here, and at the bottom the generated weak transition. The weak open transition here is the transition delivering the result of the algorithm to hole $Q$ by applying or rules: \WTUn,\WTDeux, and \WTTrois. First rule \WTUn~ adds an $\texttt{WT}_\tau$ loop on each state. Rule \WTDeux~ transforms each 3 OTs into WOTs.   Then consider application of Rule \WTTrois~ on a sequence 3  WOTs.   $\openrule
         {\{\}, True,
			(\texttt{ec}\gets \texttt{ec}+1) }
         {b1 \OTWeakarrow \tau b1}$; $\openrule
         {\{\}, True,
			(\texttt{ec}\gets \texttt{ec}+1) }
         {b1 \OTWeakarrow \tau b1}$;  $\openrule
         {\{\}, True,
			() }
         {b1 \OTWeakarrow \tau b1}$. Then Rule \WTTrois~ produces  $\openrule
         {\{\}, True,
			(\texttt{ec}\gets \texttt{ec}+2) }
         {b1 \OTWeakarrow \tau b1}$. We can  can iterate this construction an arbitrary number of times, getting for any natural number $n$ the weak open transition:
  $\openrule
         {\emptyset, True,
			(\texttt{ec}\gets \texttt{ec}+n) }
         {\text{b}1 \OTWeakarrow \tau b1} \forall n \geq 0$.  Finally,  applying again \WTTrois, and using the central open transition having \texttt{q-recv(ec)}  as $\alpha$, we get:
      $\openrule
         {\{\texttt{Q}\mapsto\texttt{q-revc(ec)}\subst{ec\gets ec+n}\}, True,
			(\texttt{ec}\gets \texttt{ec}+n) }
         {b1 \OTWeakarrow {\underline{\texttt{out(m,ec)}}\subst{ec\gets ec+n}} b0} \forall n \geq 0$. 
\end{example}

@@

%% \TODO{Eric: insert here a table with the details of the WOTs.Il manque encore au moins 3 WOT dans ce dessin...}

%% \smallskip
%% $1^st$ try, user-friendly style:

%% $$ 3 = \tau^*; \underline{in(m)}\{s1\_c:=0, s1\_m:=m\}; \tau\{s1\_c++\}^*$$

%% \smallskip
%% $2^nd$ try, full formal style ?:
%% \medskip

@@

$post_3 = (\texttt{s1\_c}\gets 0, \texttt{s1\_m}\gets \texttt{m})$

$post_4 = (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_c}\gets \texttt{s1\_c})$

$post_5 = (\texttt{m2\_c}\gets \texttt{m1\_c})$

$post_6 = (\texttt{s1\_c}\gets \texttt{m2\_c+1})$

$post_7 = (\texttt{r1\_msg}\gets \texttt{m1\_msg}, \texttt{r1\_c}\gets \texttt{m1\_c})$

@@

$Post_{456} = post_6 \shortotimes\ post_5 \shortotimes\ post_4
= (\texttt{s1\_c}\gets \texttt{s1\_c}+1)$.
\medskip

So if we denote ${Post_{456}}^*$ any iteration of this loop, we get ${Post_{456}}^* = (\texttt{s1\_c}\gets \texttt{s1\_c}+n)$ for any $n\ge 0$, and we will get e.g. the Post of the weak OT number 3' as $ post_4\shortotimes {Post_{456}}^*\shortotimes\ post_3 = (\texttt{m1\_msg}\gets m, \texttt{m1\_c}\gets n), \forall n\ge 0$
\medskip

We can now show some of the weak OTs of Figure \ref{SimpleProtCounter:SpecOA-partial} (the full table will be included in Appendix \ref{Appendix:FullExample}) :
\smallskip

$ 1 = \openrule
{\{\texttt{P}\mapsto \texttt{p\_a}\}, [\forall \texttt{m}. \texttt{p\_a} \neq \texttt{p\_send(m)} ], ()}
{000 \OTWeakarrow {\tau} 000}$

$ 2 = \openrule
{\{\texttt{Q}\mapsto \texttt{q\_b}\}, [\forall \texttt{m}. \texttt{q\_b} \neq \texttt{q\_recv(m)} ], ()}
{000 \OTWeakarrow {\tau} 000}$

$ 3 = \openrule
  {\{\texttt{P}\mapsto \texttt{p\_send(m)}\}, True,
    (\texttt{s1\_msg}\gets m, \texttt{s1\_c}\gets n)}
  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 100}
  \ \forall n\ge 0$

$ 3' = \openrule
  {\{\texttt{P}\mapsto \texttt{p\_send(m)}\}, True,
    (\texttt{m1\_msg}\gets m, \texttt{m1\_c}\gets n)}
  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 210}
  \ \forall n\ge 0$

$ 3'' = \openrule
  {\{\texttt{P}\mapsto \texttt{p\_send(m)}\}, True, 
    (\texttt{m2\_c}\gets n)}
  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 220}
  \ \forall n\ge 0$

         $ 4 = \openrule
         {\{\}, True, (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_c}\gets \texttt{s1\_c}+n)}
         {100 \OTWeakarrow {\tau} 210}
         \ \forall n\ge 0$

$ 5 = \openrule
         {\{\}, True, (\texttt{m2\_c}\gets \texttt{m1\_c}+n)}
         {210 \OTWeakarrow {\tau} 220}
         \ \forall n\ge 0$

$ 6 = \openrule
         {\{\}, True, (\texttt{s1\_c}\gets \texttt{m2\_c}+n)}
         {220 \OTWeakarrow {\tau} 100}
         \ \forall n\ge 0$

$ 7 = \openrule
         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_c}\gets \texttt{s1\_c}+n)}
         {100 \OTWeakarrow {\tau} 201}
         \ \forall n\ge 0$

$ 7' = \openrule
         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{m1\_msg}, \texttt{r1\_c}\gets \texttt{m1\_c}+n)}
         {210 \OTWeakarrow {\tau} 201}
         \ \forall n\ge 0$

$ 7'' = \openrule
         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{m1\_msg}, \texttt{r1\_c}\gets \texttt{m2\_c}+n)}
         {220 \OTWeakarrow {\tau} 201}
         \ \forall n\ge 1$

$ 8 = \openrule
         {\{\}, True, ()}
         {201 \OTWeakarrow {\underline{\texttt{out(m,c)}}\subst{(m\gets \texttt{r1\_msg}, c\gets \texttt{r1\_c}}} 202}
         $

\newpage
\subsection{Composition properties: composition of weak open transitions}
We now have two different semantics for open pNets: a strong semantics, defined  as an open automaton, and as a weak semantics, defined as a weak open automaton. Like the open automaton, the weak open automaton features valuable composition properties. We can exhibit  a composition property and a decomposition property that relate open pNet composition with their semantics, defined as weak open automata. These are however technically more complex than the ones for open automata because each hole performs a set of actions, and thus a composed transition is the composition of one transition of the top-level pNet and a sequence of transitions of the sub-pNet that fills its hole. They can be found as Lemmas~\ref{lem-decomposeWOT}, Lemma~\ref{lem-Weakcompose1}, and Lemma~\ref{lem-Weakcompose} in~\ref{sec:app-composition}.

@@

state a0
transition m_recv(msg,c) -> a1 {a1_msg:=msg, a1_c:=c}

state a1
vars a1_msg:Data a1_c:Int
transition m_send(a1_msg, a1_c) -> a0 
transition synchro($tau) -> a2

@@

state s0
transition s_recv(msg) -> s1 {s1_msg:=msg, s1_c:=0}

state s1
vars s1_msg:Data s1_c:Int
transition s_send(s1_msg, s1_c) -> s2 {s2_c:=s1_c}

state s2
vars  s2_c:Int
transition $s_ack -> s0
transition $s_error -> s1 {s1_c:=s2_c+1}

@@

state r0
transition r_recv(msg,c) -> r1 {r1_msg:=msg, r1_c:=c}

state r1
vars r1_msg:Data r1_c:Int
transition r_send(r1_msg, r1_c) -> r2

@@

%% \begin{lstlisting}[basicstyle=\scriptsize\ttfamily, language=java, frame=single]
%% SimpleProtImpl2
%% --------------------
%% SV6 SVs: <p_send(m), in(m), _>-->in(m)
%% SV7 SVs: <p_a, _, _>-->p_a, p_a!=(p_send(m))
%% SV8 SVs: <_, out(m, c), q_recv(m, c)>-->out(m, c)
%% SV9 SVs: <_, _, q_a>-->q_a, q_a!=(q_recv(m, c))
%% SV11 SVs: <_, _tau_, _>-->_tau_
%% Holes: P
%% Subnets: medium
%% - medium
%% - SV0 SVs: <in(m), _, _>-->in(m)
%% - SV1 SVs: <s_send(m, c), m_recv(m, c), _>-->_tau_
%% - SV2 SVs: <_, m_send(m), r_recv(m)>-->_tau_
%% - SV3 SVs: <s_ack, _, r_ack>-->_tau_
%% - SV4 SVs: <s_error, m_error, _>-->_tau_
%% - SV5 SVs: <_, _, out(m, c)>-->out(m, c)
%% - SV10 SVs: <_, _tau_, _>-->_tau_
%% - pLTS: Sender
%% - - Transition: s0---in(msg)-->s1, { s1_msg := msg s1_c := 0}
%% - - Transition: s1---s_send(s1_msg, s1_c)-->s2, {}
%% - - Transition: s2---s_ack-->s0, {}
%% - - Transition: s2---s_error-->s1, { s1_c := s2_c+1}
%% - - Variable: s1_c, State: s1, Value(s) = 0,s2_c+1,
%% - - Variable: s1_msg, State: s1, Value(s) = msg,
%% - pLTS: M1
%% - - Transition: a0---m_recv(msg, c)-->a1, { a1_msg := msg a1_c := c}
%% - - Transition: a1---m_send(a1_msg, a1_c)-->a0, {}
%% - - Transition: a1---_tau_-->a2, {}
%% - - Transition: a2---m_error-->a0, {}
%% - - Variable: a1_msg, State: a1, Value(s) = msg,
%% - - Variable: a1_c, State: a1, Value(s) = c,
%% - pLTS: Receiver
%% - - Transition: r0---r_recv(msg, c)-->r1, { r1_msg := msg r1_c := c}
%% - - Transition: r1---out(r1_msg, r1_c)-->r2, {}
%% - - Transition: r2---r_ack-->r0, {}
%% - - Variable: r1_msg, State: r1, Value(s) = msg,
%% - - Variable: r1_c, State: r1, Value(s) = c,
%% Holes: Q
%% \end{lstlisting}

@@

{P|->p_send(m:SV6:1:1)},
[(msg=m:SV0:12:1)/\((s_recv(msg))=(s_recv(m:SV0:12:1)))], {s1_msg := msg, s1_c := 0}
	OT:1 ------------------------------------------------------------
		<s0_a0_r0>-----_in(m:SV6:1:1)_----><s1_a0_r0>

@@

{},   [(s1_msg=m:SV1:114:2)/\(s1_c=c:SV1:114:2)
  /\((s_send(s1_msg, s1_c))=(s_send(m:SV1:114:2, c:SV1:114:2)))
  /\(msg=m:SV1:114:2)/\(c=c:SV1:114:2)
  /\((m_recv(msg, c))=(m_recv(m:SV1:114:2, c:SV1:114:2)))],
{s2_c := s1_c, a1_msg := msg, a1_c := c}
	OT:6 ------------------------------------------------------------
		<s1_a0_r0>-----_tau_----><s2_a1_r0>

@@

{},   [(a1_msg=m:SV2:114:3)/\(a1_c=c:SV2:114:3)
  /\((m_send(a1_msg, a1_c))=(m_send(m:SV2:114:3, c:SV2:114:3)))
  /\(msg=m:SV2:114:3)/\(c=c:SV2:114:3)
  /\((r_recv(msg, c))=(r_recv(m:SV2:114:3, c:SV2:114:3)))],
{r1_msg := msg, r1_c := c}
	OT:9 ------------------------------------------------------------
		<s2_a1_r0>-----_tau_----><s2_a0_r1>

@@

{Q|->q_recv(m:SV8:1:3, c:SV8:1:3)},
[(r1_msg=m:SV5:18:6)/\(r1_c=c:SV5:18:6)
  /\((r_send(r1_msg, r1_c))=(r_send(m:SV5:18:6, c:SV5:18:6)))],   {}
	OT:12 ------------------------------------------------------------
		<s2_a0_r1>-----_out(m:SV8:1:3, c:SV8:1:3)_----><s2_a0_r2>

@@

		{},   [],   {s1_c := s2_c+1}
	OT:16 --------------------------------------
		<s2_a2_r0>-----_tau_----><s1_a0_r0>

@@

Global State: <s1_a0_r0>
===================
pLTS States: <s1 vars: { s1_msg <-{msg} s1_c <-{0, s2_c+1}}> <a0 vars: {}> <r0 vars: {}>

Global State: <s2_a1_r0>
===================
pLTS States: <s2 vars: { s2_c <-{s1_c}}> <a1 vars: { a1_msg <-{msg} a1_c <-{c}}> <r0 vars: {}>

Global State: <s2_a0_r1>
===================
pLTS States: <s2 vars: { s2_c <-{s1_c}}> <a0 vars: {}> <r1 vars: { r1_c <-{c} r1_msg <-{msg}}>

Global State: <s2_a2_r0>
===================
pLTS States: <s2 vars: { s2_c <-{s1_c}}> <a2 vars: {}> <r0 vars: {}>

Global State: <s2_a0_r2>
===================
pLTS States: <s2 vars: { s2_c <-{s1_c}}> <a0 vars: {}> <r2 vars: {}>

@@

>>>>

Fig. \ref{SimpleProt:Spec} (left) shows the example principle: two unspecified
processes $P$ and $Q$ (holes) communicate messages, with a data value
argument, through the two protocol entities. Process $P$ send an $\texttt{p-send(m)}$ message to the $Sender$; this communication is denoted as $\texttt{\underline{in(m)}}$, where underline actions represent internal actions (similar to the $\tau$ of CCS), that cannot be further synchronised with the environment. At the other end process $Q$ receives the message from the $Receiver$. The holes $P$ and $Q$ can also have other interactions with their environment, represented here by actions $\texttt{p-a}$ and $\texttt{q-b}$. The underlying network is modelled by a medium entity transporting messages from the sender to the receiver, and that is able to detect transport errors, and signal them to the sender. The return $ack$ message from $receiver$ to $sender$ is supposed to be safe. The final transmission of the message to the recipient (the hole Q) includes the value of the ``error counter'' $ec$.

Fig. \ref{SimpleProt:Spec} (right) shows a graphical view of the pNet of the system \emph{specification}:
the full system should be equivalent (e.g. through weak bisimulation)
to the two processes connected simply through a perfect medium.  
The pNet has a tree-like structure.  The root node of the tree {\it SimpleSystemSpec} is the top level of the pNet structure. It acts as the parallel operator. It consists of tree nodes: two Holes $P$ and $Q$ and one subnet, noted {\it PrefectBuffer}. Nodes of the tree are synchronized using four synchronization vectors, that  express the possible synchronization between the parameterized actions of a subset of the nodes. For instance, in the vector "$< \texttt{p-send(m)},\texttt{in(m)},\_> \rightarrow \texttt{\underline{in(m)}}$ only $P$ and {\it PrefectBuffer} nodes are involved in the synchronization. More precisely, the synchronization between these processes occurs when  process $P$  performs $\texttt{p-send(m)}$  action sending a message, and  the medium accepts the message through $\texttt{in(m)}$ action  at the same time. And the result that will be returned at upper level is the internal action  $\texttt{\underline{in(m)}}$.

@@

\begin{example}
  Figure \ref{WOT2} shows the construction of one of the weak transitions of the Specification OA. On the top we show the subset of the original open automaton (from Figure \ref{SimpleProtCounter:SpecOA}) considered here, and at the bottom the generated weak transition. The weak open transition shown here is the transition delivering the result of the algorithm to hole $Q$ by applying rules: \WTUn,\WTDeux, and \WTTrois. First rule \WTUn~ adds an $\texttt{WT}_\tau$ loop on each state. Rule \WTDeux~ transforms each 3 OTs into WOTs.   Then consider application of Rule \WTTrois~ on a sequence 3  WOTs.   $\openrule
         {\{\}, True,
			(\texttt{ec}\gets \texttt{ec}+1) }
         {b1 \OTWeakarrow \tau b1}$; $\openrule
         {\{\}, True,
			(\texttt{ec}\gets \texttt{ec}+1) }
         {b1 \OTWeakarrow \tau b1}$;  $\openrule
         {\{\}, True,
			() }
         {b1 \OTWeakarrow \tau b1}$. Then Rule \WTTrois~ produces  $\openrule
         {\{\}, True,
			(\texttt{ec}\gets \texttt{ec}+2) }
         {b1 \OTWeakarrow \tau b1}$. We can  can iterate this construction an arbitrary number of times, getting for any natural number $n$ the weak open transition:
  $\openrule
         {\emptyset, True,
			(\texttt{ec}\gets \texttt{ec}+n) }
         {\text{b}1 \OTWeakarrow \tau b1} \forall n \geq 0$.  Finally,  applying again \WTTrois, and using the central open transition having \texttt{q-recv(ec)}  as $\alpha$, we get:
      $\openrule
         {\{\texttt{Q}\mapsto\texttt{q-revc(ec)}\subst{ec\gets ec+n}\}, True,
			(\texttt{ec}\gets \texttt{ec}+n) }
         {b1 \OTWeakarrow {\underline{\texttt{out(m,ec)}}\subst{ec\gets ec+n}} b0} \forall n \geq 0$. 
\end{example}

@@

@@

$post_3 = (\texttt{s1\_ec}\gets 0, \texttt{s1\_m}\gets \texttt{m})$

$post_4 = (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec})$

$post_5 = (\texttt{m2\_ec}\gets \texttt{m1\_ec})$

$post_6 = (\texttt{s1\_ec}\gets \texttt{m2\_ec+1})$

$post_7 = (\texttt{r1\_msg}\gets \texttt{m1\_msg}, \texttt{r1\_ec}\gets \texttt{m1\_ec})$

@@

$Post_{456} = post_6 \shortotimes\ post_5 \shortotimes\ post_4
= (\texttt{s1\_ec}\gets \texttt{s1\_ec}+1)$.
\medskip

So if we denote ${Post_{456}}^*$ any iteration of this loop, we get ${Post_{456}}^* = (\texttt{s1\_ec}\gets \texttt{s1\_ec}+n)$ for any $n\ge 0$, and we will get e.g. the Post of the weak OT number 3' as $ post_4\shortotimes {Post_{456}}^*\shortotimes\ post_3 = (\texttt{m1\_msg}\gets m, \texttt{m1\_ec}\gets n), \forall n\ge 0$
\medskip

We can now show some of the weak OTs of Figure \ref{SimpleProtCounter:SpecOA-partial} (the full table is included in Appendix \ref{Appendix:FullExample}) :
\smallskip

$ 1 = \openrule
{\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{m}. \texttt{p-a} \neq \texttt{p-send(m)} ], ()}
{000 \OTWeakarrow {\tau} 000}$

$ 3' = \openrule
  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
    (\texttt{m1\_msg}\gets m, \texttt{m1\_ec}\gets n)}
  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 210}
  \ \forall n\ge 0$

         $ 4 = \openrule
         {\{\}, True, (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}+n)}
         {100 \OTWeakarrow {\tau} 210}
         \ \forall n\ge 0$

$ 8 = \openrule
         {\{\}, True, ()}
         {201 \OTWeakarrow {\underline{\texttt{out(m,c)}}\subst{(m\gets \texttt{r1\_msg}, c\gets \texttt{r1\_ec}}} 202}
         $

\subsection{Composition properties: composition of weak open transitions}
We now have two different semantics for open pNets: a strong semantics, defined  as an open automaton, and as a weak semantics, defined as a weak open automaton. Like the open automaton, the weak open automaton features valuable composition properties. We can exhibit  a composition property and a decomposition property that relate open pNet composition with their semantics, defined as weak open automata. These are however technically more complex than the ones for open automata because each hole performs a set of actions, and thus a composed transition is the composition of one transition of the top-level pNet and a sequence of transitions of the sub-pNet that fills its hole. They can be found as Lemmas~\ref{lem-decomposeWOT}, Lemma~\ref{lem-Weakcompose1}, and Lemma~\ref{lem-Weakcompose} in~\ref{sec:app-composition}.

@@

state a0
transition m_recv(msg,c) -> a1 {a1_msg:=msg, a1_ec:=c}

state a1
vars a1_msg:Data a1_ec:Int
transition m_send(a1_msg, a1_ec) -> a0 
transition synchro($tau) -> a2

@@

state s0
transition s_recv(msg) -> s1 {s1_msg:=msg, s1_ec:=0}

state s1
vars s1_msg:Data s1_ec:Int
transition s_send(s1_msg, s1_ec) -> s2 {s2_ec:=s1_ec}

state s2
vars  s2_ec:Int
transition $s_ack -> s0
transition $s_error -> s1 {s1_ec:=s2_ec+1}

@@

state r0
transition r_recv(msg,c) -> r1 {r1_msg:=msg, r1_ec:=c}

state r1
vars r1_msg:Data r1_ec:Int
transition r_send(r1_msg, r1_ec) -> r2

@@

%% \begin{lstlisting}[basicstyle=\scriptsize\ttfamily, language=java, frame=single]
%% SimpleProtImpl2
%% --------------------
%% SV6 SVs: <p_send(m), in(m), _>-->in(m)
%% SV7 SVs: <p_a, _, _>-->p_a, p_a!=(p_send(m))
%% SV8 SVs: <_, out(m, c), q_recv(m, c)>-->out(m, c)
%% SV9 SVs: <_, _, q_a>-->q_a, q_a!=(q_recv(m, c))
%% SV11 SVs: <_, _tau_, _>-->_tau_
%% Holes: P
%% Subnets: medium
%% - medium
%% - SV0 SVs: <in(m), _, _>-->in(m)
%% - SV1 SVs: <s_send(m, c), m_recv(m, c), _>-->_tau_
%% - SV2 SVs: <_, m_send(m), r_recv(m)>-->_tau_
%% - SV3 SVs: <s_ack, _, r_ack>-->_tau_
%% - SV4 SVs: <s_error, m_error, _>-->_tau_
%% - SV5 SVs: <_, _, out(m, c)>-->out(m, c)
%% - SV10 SVs: <_, _tau_, _>-->_tau_
%% - pLTS: Sender
%% - - Transition: s0---in(msg)-->s1, { s1_msg := msg s1_ec := 0}
%% - - Transition: s1---s_send(s1_msg, s1_ec)-->s2, {}
%% - - Transition: s2---s_ack-->s0, {}
%% - - Transition: s2---s_error-->s1, { s1_ec := s2_ec+1}
%% - - Variable: s1_ec, State: s1, Value(s) = 0,s2_ec+1,
%% - - Variable: s1_msg, State: s1, Value(s) = msg,
%% - pLTS: M1
%% - - Transition: a0---m_recv(msg, c)-->a1, { a1_msg := msg a1_ec := c}
%% - - Transition: a1---m_send(a1_msg, a1_ec)-->a0, {}
%% - - Transition: a1---_tau_-->a2, {}
%% - - Transition: a2---m_error-->a0, {}
%% - - Variable: a1_msg, State: a1, Value(s) = msg,
%% - - Variable: a1_ec, State: a1, Value(s) = c,
%% - pLTS: Receiver
%% - - Transition: r0---r_recv(msg, c)-->r1, { r1_msg := msg r1_ec := c}
%% - - Transition: r1---out(r1_msg, r1_ec)-->r2, {}
%% - - Transition: r2---r_ack-->r0, {}
%% - - Variable: r1_msg, State: r1, Value(s) = msg,
%% - - Variable: r1_ec, State: r1, Value(s) = c,
%% Holes: Q
%% \end{lstlisting}

@@

{P|->p_send(m:SV6:1:1)},
[(msg=m:SV0:12:1)/\((s_recv(msg))=(s_recv(m:SV0:12:1)))], {s1_msg := msg, s1_ec := 0}
	OT:1 ------------------------------------------------------------
		<s0_a0_r0>-----_in(m:SV6:1:1)_----><s1_a0_r0>

@@

{},   [(s1_msg=m:SV1:114:2)/\(s1_ec=c:SV1:114:2)
  /\((s_send(s1_msg, s1_ec))=(s_send(m:SV1:114:2, c:SV1:114:2)))
  /\(msg=m:SV1:114:2)/\(c=c:SV1:114:2)
  /\((m_recv(msg, c))=(m_recv(m:SV1:114:2, c:SV1:114:2)))],
{s2_ec := s1_ec, a1_msg := msg, a1_ec := c}
	OT:6 ------------------------------------------------------------
		<s1_a0_r0>-----_tau_----><s2_a1_r0>

@@

{},   [(a1_msg=m:SV2:114:3)/\(a1_ec=c:SV2:114:3)
  /\((m_send(a1_msg, a1_ec))=(m_send(m:SV2:114:3, c:SV2:114:3)))
  /\(msg=m:SV2:114:3)/\(c=c:SV2:114:3)
  /\((r_recv(msg, c))=(r_recv(m:SV2:114:3, c:SV2:114:3)))],
{r1_msg := msg, r1_ec := c}
	OT:9 ------------------------------------------------------------
		<s2_a1_r0>-----_tau_----><s2_a0_r1>

@@

{Q|->q_recv(m:SV8:1:3, c:SV8:1:3)},
[(r1_msg=m:SV5:18:6)/\(r1_ec=c:SV5:18:6)
  /\((r_send(r1_msg, r1_ec))=(r_send(m:SV5:18:6, c:SV5:18:6)))],   {}
	OT:12 ------------------------------------------------------------
		<s2_a0_r1>-----_out(m:SV8:1:3, c:SV8:1:3)_----><s2_a0_r2>

@@

		{},   [],   {s1_ec := s2_ec+1}
	OT:16 --------------------------------------
		<s2_a2_r0>-----_tau_----><s1_a0_r0>

@@

Global State: <s1_a0_r0>
===================
pLTS States: <s1 vars: { s1_msg <-{msg} s1_ec <-{0, s2_ec+1}}> <a0 vars: {}> <r0 vars: {}>

Global State: <s2_a1_r0>
===================
pLTS States: <s2 vars: { s2_ec <-{s1_ec}}> <a1 vars: { a1_msg <-{msg} a1_ec <-{c}}> <r0 vars: {}>

Global State: <s2_a0_r1>
===================
pLTS States: <s2 vars: { s2_ec <-{s1_ec}}> <a0 vars: {}> <r1 vars: { r1_ec <-{c} r1_msg <-{msg}}>

Global State: <s2_a2_r0>
===================
pLTS States: <s2 vars: { s2_ec <-{s1_ec}}> <a2 vars: {}> <r0 vars: {}>

Global State: <s2_a0_r2>
===================
pLTS States: <s2 vars: { s2_ec <-{s1_ec}}> <a0 vars: {}> <r2 vars: {}>

@@

\begin{figure}[h]
   \centerline{\includegraphics[width=9cm]{XFIG/SimpleProtImpl-WOA}}
  \caption{Weak Open Automaton of the implementation}
   \label{Appendix:SpecOA-partial}
\end{figure}

In Figure \ref{Appendix:SpecOA-partial} we show the weak oepn automaton of our implementation pNet. Details of the weak transitions is listed here:

$ 1 = \openrule
{\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{m}. \texttt{p-a} \neq \texttt{p-send(m)} ], ()}
{000 \OTWeakarrow {\tau} 000}$

$ 2 = \openrule
{\{\texttt{Q}\mapsto \texttt{q-b}\}, [\forall \texttt{m}. \texttt{q-b} \neq \texttt{q-recv(m)} ], ()}
{000 \OTWeakarrow {\tau} 000}$

$ 3 = \openrule
  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
    (\texttt{s1\_msg}\gets m, \texttt{s1\_ec}\gets n)}
  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 100}
  \ \forall n\ge 0$

$ 3' = \openrule
  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
    (\texttt{m1\_msg}\gets m, \texttt{m1\_ec}\gets n)}
  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 210}
  \ \forall n\ge 0$

$ 3'' = \openrule
  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True, 
    (\texttt{m2\_ec}\gets n)}
  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 220}
  \ \forall n\ge 0$

         $ 4 = \openrule
         {\{\}, True, (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}+n)}
         {100 \OTWeakarrow {\tau} 210}
         \ \forall n\ge 0$

$ 5 = \openrule
         {\{\}, True, (\texttt{m2\_ec}\gets \texttt{m1\_ec}+n)}
         {210 \OTWeakarrow {\tau} 220}
         \ \forall n\ge 0$

$ 6 = \openrule
         {\{\}, True, (\texttt{s1\_ec}\gets \texttt{m2\_ec}+n)}
         {220 \OTWeakarrow {\tau} 100}
         \ \forall n\ge 0$

$ 7 = \openrule
         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{s1\_ec}+n)}
         {100 \OTWeakarrow {\tau} 201}
         \ \forall n\ge 0$

$ 7' = \openrule
         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{m1\_msg}, \texttt{r1\_ec}\gets \texttt{m1\_ec}+n)}
         {210 \OTWeakarrow {\tau} 201}
         \ \forall n\ge 0$

$ 7'' = \openrule
         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{m1\_msg}, \texttt{r1\_ec}\gets \texttt{m2\_ec}+n)}
         {220 \OTWeakarrow {\tau} 201}
         \ \forall n\ge 1$

$ 8 = \openrule
         {\{\}, True, ()}
         {201 \OTWeakarrow {\underline{\texttt{out(m,c)}}\subst{(m\gets \texttt{r1\_msg}, c\gets \texttt{r1\_ec}}} 202}
         $
